Dependent Object Types

### 2012-08-05 article.tex
bib

This paper presents a proposal for a new type-theoretic foundation of
Scala and languages like it. The properties we are interested in
modelling are Scala's path-dependent types and abstract type members,
as well as its mixture of nominal and structural typing through the
use of refinement types. Compared to previous approaches (nuObj, FS),
we make no attempt to model inheritance or mixin composition. Indeed
we will argue that such concepts are better modelled in a different
setting.

@@

We prove that the DOT calculus is type-safe using logical relations in
section~\ref{dot-type-safety}. However, we first tried to prove the
calculus type-safe using the standard theorems of preservation and
progress. Unfortunately, for the calculus as presented, and any of its
variants that we devised, preservation doesn't hold. In this section,
we review some of the most salient counterexamples to preservation
that we found. These counterexamples have been checked with PLT Redex.

@@

\section{Type Safety via Logical Relations}\label{dot-type-safety}

@@

We added path equality provisions in the subtyping rules, in the same
spirit as the Tribe calculus.

>>>>

This paper presents a proposal for a new type-theoretic foundation of
Scala and languages like it. The properties we are interested in
modelling are Scala's path-dependent types and abstract type members,
as well as its mixture of nominal and structural typing through the
use of refinement types. Compared to previous approaches~\cite{nuObj,FS},
we make no attempt to model inheritance or mixin composition. Indeed
we will argue that such concepts are better modelled in a different
setting.

@@

We prove that the DOT calculus is type-safe using logical relations in
section~\ref{dot-type-safety}. However, we first tried to prove the
calculus type-safe using the standard theorems of preservation and
progress~\cite{soundness,tapl}. Unfortunately, for the calculus as
presented, and any of its variants that we devised, preservation
doesn't hold. In this section, we review some of the most salient
counterexamples to preservation that we found. These counterexamples
have been checked with PLT Redex.

@@

\section{Type Safety via Logical Relations}\label{dot-type-safety}
We prove type-safety of the DOT calculus via step-indexed logical
relations~\cite{ahmed04,ahmed06,step_indexed_obj}.

@@

We added path equality provisions in the subtyping rules, in the same
spirit as the Tribe calculus~\cite{tribe}.
